{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2024-12-19 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes, a lot

    \subsection{Contributions}
        Our contributions are two folds, theoretical and practical. 
        Nesterov's acceleration extrapolate $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} = (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''. 
        The choices for $\theta_k$ varies. 
        In Chamboolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ gives strong weak convergence of the iterates $x_k$ in Hilbert space. 
        In Beck \cite{beck_first-order_2017}, it has constant $\theta_t = (\sqrt{\kappa} - 1)/(\sqrt{\kappa} + 1)$ where $\kappa = \mu/L$. 
        \par
        Firstly, we relaxed the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:example_algorithm} and showed an upper bound of the optimal gap. 
        Let $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$, given any $\gamma_1 \in (0, L]$ and define $\alpha_1$ by 
        \begin{align*}
            \alpha_1 = \frac{1}{2}\left(
                \frac{\mu}{L} - \frac{\gamma_1}{L} + 
                \sqrt{
                    \left(
                        \frac{\gamma_1}{L} - \frac{\mu}{L}
                    \right)^2 + 
                    \frac{4\gamma_1}{L}
                }
            \right). 
        \end{align*}
        We define $\alpha_k$ for $k \ge 2$ by: 
        \begin{align*}
            &\alpha_k \in (0, 1), 
            \\
            & 0 < \rho_k \alpha_k^2 < 1, 
            \\
            &\alpha_{k + 1} = 
            \frac{1}{2}\left(
                \frac{\mu}{L} - \rho_{k}\alpha_{k}^2 
                +
                \sqrt{(\rho_{k}\alpha_{k}^2 - \mu/L)^2 + 4\rho_{k}\alpha_{k}^2}
            \right). 
        \end{align*}
        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed (Definition \ref{def:wapg}), we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
        \begin{align*}
            \mathcal O\left(
                \left(
                    \prod_{i = 1}^{k - 1} \max(1, \rho_{k})
                \right)
                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
            \right). 
        \end{align*}
        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces perfectly to the a variant proposed in Chambolle Dossal \cite{chambolle_convergence_2015}. 
        And when $\rho_k = 1$, R-WAPG reduces perfectly to V-FISTA by Beck \cite{beck_first-order_2017}, and it produces convergence claim consistent with the literatures. 
        We will also present a simplified convergence rate when $\rho_k \in (0, \alpha_{k - 1}^2), \mu = 0$ which is also consistent with the literatures. 
        \par
        Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG''. 
        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ with minimal computational cost. 
        We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart. 
    \subsection{Prior works}

@@

\section{Formulation of R-WAPG and its convergence rates}
    The sole focus of this section is Definition \ref{def:wapg}.
    It describes the R-WAPG algorithm which generates iterates $(x_k, y_k, v_k)$ and admits potential convergence claim using Proposition \ref{prop:stepwise-lyapunov}. 
    It introduces the procedures of making the sequence $\alpha_k \in (0, 1)$ which assists with claiming convergence of the algorithm using Proposition \ref{prop:stepwise-lyapunov} by connecting them together. 
    \begin{definition}[R-WAPG sequence]\label{def:rwapg-seq}
        Assume $0 \le \mu < L$. 
        For any $\gamma_1 \in (0, L]$, define $\alpha_1 = (1 - \alpha_1)\gamma_1 + \mu \alpha_1$. 
        Then the sequence $(\alpha_{k})_{k \ge 1}, (\rho_k)_{k \ge 1}$ satisfy for all $k \ge 2$: 
            &\alpha_k \in (0, 1), 
            & 0 < \rho_k \alpha_k^2 < 1, 
            &L\alpha_k^2 = (1 - \alpha_k)\rho_{k - 1}L \alpha_{k - 1}^2 + \mu \alpha_k. 
    \begin{observation}\label{obs:r-wapg-observation-1}
        If $\alpha_1 \in (0, 1)$ which is true by $\gamma_1 \in (0, L]$, then the entire sequence $\alpha_k \in (0, 1)$. 
        Suppose inductively that $\alpha_{k - 1}, \rho_{k - 1}$ are given such that they satisfy $\alpha_{k -1} \in (0, 1)$ and $0 < \rho_{k - 1} \alpha_{k - 1}^2 < 1$. 
        Solving the quadratic $L\alpha_k^2=(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2 + \mu \alpha_k$ for $\alpha_k$ yields candidates. 
            \alpha_k &= 
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                \pm
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
        Choosing the positive sign which is the larger one of the roots of the quadratic. 
        We have $\alpha_k > 0$ because: 
            \alpha_k &=
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                \left|\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L\right|
            \right) + \alpha_{k - 1}\sqrt{\rho_{k - 1}}
            & > 0. 
        On the last strict inequality we used the fact that $\rho_{k - 1}> 0, \alpha_{k - 1} > 0$. 
        An upper bound can be identified by using inductive hypothesis and considering: 
            \alpha_k &= 
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
            &<
                \frac{\mu}{L} + 
                \sup_{x \in (0, 1)}
                \left\lbrace
                    -x + \sqrt{(x - \mu/L)^2 + 4x}
                \right\rbrace
            & \le \frac{1}{2}\left(
                \mu/L + \max\left(\mu/L, -1 + \sqrt{(1 - \mu/L)^2 + 4}\right)
            \right) \le 1. 
        Going to the first inequality, we used $\rho_{k - 1} \alpha_{k - 1}^2 < 1$ to get the strict inequality. 
        Going from the second to the third inequality, we maximized $\mu/L$ by monotone increasing of linear function and the square root function. 
        Therefore, inductively, $\alpha_k \in (0, 1)$ holds. 
        However, the limit of $\alpha_k$ could be 1. 

@@

        Let $(\alpha_k)_{k \ge1}, (\rho_k)_{k \ge 1}$ be given by Definition \ref{def:rwapg-seq}. 

@@

            \gamma_k &:= \left.\begin{cases}
                \rho_{k -1}L\alpha_{k - 1}^2 & k \ge 2,
                \gamma_1 & k = 1. 
            \end{cases}\right\rbrace,
            \hat \gamma_{k + 1} & = (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2

@@

    \begin{observation}

@@

        The algorithm chains together the sequence of $(\hat \gamma_{k+1})_{k \ge 1}$ and $(\gamma_k)_{k \ge 1}$ in Definition \ref{prop:stepwise-lyapunov} through the equalities: 
            \hat \gamma_{k + 1} = L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \alpha_k \mu
            &= (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu. 

@@

                \prod_{i = 1}^{k - 1} \max(1, \rho_{k})

@@

        Since $\hat \gamma_2, \gamma_1$ has $\hat \gamma_2 = (1 - \alpha_1)\gamma_1 + \mu \alpha_1$ and $R_2$ is defined in the same manner as in Proposition \ref{prop:stepwise-lyapunov}, we can invoke Proposition \ref{prop:stepwise-lyapunov} and it gives: 
            F(x_{2}) - F(x^*) + R_2 + \frac{L \alpha_k^2}{2}\Vert v_{2} - x^*\Vert^2

@@

@@

        Next, for all $k = 2, 3, \cdots, N$, the R-WAPG described in \ref{def:wapg} has $\hat \gamma_{k + 1} = L\alpha_{k - 1}^2 = (1 - \alpha_k)\gamma_k + \mu\alpha_k$. 
        We have also $\alpha_k \in (0, 1)$ by Observation \ref{obs:r-wapg-observation-1}. 

@@

        The description of $R_k$ is the same as in Proposition \ref{prop:stepwise-lyapunov} hence we can use Proposition \ref{prop:stepwise-lyapunov}, to show that for all $k \ge 1$: 

@@

            &F(x_{k + 1}) - F^* + R_{k + 1} + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2

@@

            & F(x_{k + 1}) - F^* +

@@

    \subsection{Narrowing it down}
        \begin{proposition}[First equivalent representation of R-WAPG]\label{prop:wapg-first-equivalent-repr}\;\\
            Assume $\mu < L$. 
            Choose any $\gamma_1 \in (0, L], x_1, v_1$ as the initial condition for R-WAPG (Definition \ref{def:wapg}) to produce vectors sequence $(y_k, v_{k + 1}, x_{k + 1})_{k \ge 1}$. 
            Then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge1}$, and for all $k\ge 1$ they are algebraically equivalent to
            \begin{align*}
                & 
                y_{k} = 
                \left(
                    1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
                \right)^{-1}
                \left(
                    v_{k} + 
                    \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
                \right), 
                \\
                & x_{k + 1} = 
                y_k - L^{-1} \mathcal G_L y_k, 
                \\
                & v_{k + 1} = 
                \left(
                    1 + \frac{\mu}{L \alpha_k - \mu}
                \right)^{-1}
                \left(
                    v_k + 
                    \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
            \end{align*}

@@

            On the third $\iff$, we can assume $\alpha_k \neq \mu/L\; \forall k \ge 2$ because if $\alpha_k = \mu/L$ were impossible, it then has
                (1 - \alpha_k)L \rho_{k - 1}\alpha_{k - 1}^2 = 0 \implies \alpha_{k - 1} = 0. 
            Which contradict $\alpha_{k - 1} \in (0, 1)\; \forall k \ge 2$ because $\alpha_1 \in (0, 1)$ is given to satisfy the condition in the base case, and $\alpha_k \in (0, 1)\; \forall k \ge 2$ by justifications in Observation \ref{obs:r-wapg-observation-1}. 

@@

            Given any $\gamma_1 \in (0, L]$, $(x_1, v_1)$. 
            Define 
                \alpha_1 = \frac{1}{2}\left(
                    \frac{\mu}{L} - \frac{\gamma_1}{L} + 
                    \sqrt{
                            \frac{\gamma_1}{L} - \frac{\mu}{L}
                        \right)^2 + 
                        \frac{4\gamma_1}{L}
            For $k = 1, 2, \cdots $, the algorithm generates sequence of vector iterates $(y_{k}, v_{k + 1}, x_{k + 1})_{k \ge 1}$ and auxiliary sequence $(\alpha_{k + 1}, \rho_k)_{k \ge 1}$ by the procedures: 

@@

                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k
                & \text{choose any } \rho_{k}: 0 < \rho_{k} < \alpha_{k}^{-2}, 
                & \alpha_{k + 1} := 
                \frac{\mu}{L} - \rho_{k}\alpha_{k}^2 
                \sqrt{(\rho_{k}\alpha_{k}^2 - \mu/L)^2 + 4\rho_{k}\alpha_{k}^2}

@@

            Let iterates $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge1}$ be given by Definition \ref{def:r-wapg-intermediate}. 

@@

            We note that $x_1, v_1, y_1$ may not satisfy the inequalities since, 

@@

        Given any initial $L \in (0, L]$, $(x_1, v_1)$. 

@@

        Define $\alpha_1$ by 
            \alpha_1 = \frac{1}{2}\left(
                \frac{\mu}{L} - \frac{\gamma_1}{L} + 
                \sqrt{
                        \frac{\gamma_1}{L} - \frac{\mu}{L}
                    \right)^2 + 
                    \frac{4\gamma_1}{L}

@@

            x_{k + 1} + (\alpha_k^{-1} -1)(x_{k + 1} - x_k), 
            & \text{choose any }   \rho_{k}: 0 < \rho_{k} < \alpha_{k}^{-2}, 
            &\alpha_{k + 1} = 
            \frac{\mu}{L} - \rho_{k}\alpha_{k}^2 
            \sqrt{(\rho_{k}\alpha_{k}^2 - \mu/L)^2 + 4\rho_{k}\alpha_{k}^2}

@@

    \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
        Let $y_1 = x_1$. 
        Given any $\gamma_1 \in (0, L]$, initialize any $\alpha_1 \in (0, 1)$ by: 
        \begin{align*}
            \alpha_1 = \frac{1}{2}\left(
                \frac{\mu}{L} - \frac{\gamma_1}{L} + 
                \sqrt{
                    \left(
                        \frac{\gamma_1}{L} - \frac{\mu}{L}
                    \right)^2 + 
                    \frac{4\gamma_1}{L}
                }
            \right). 
        \end{align*}
        For $k = 1, 2, \cdots $, the algorithm generates iterates $x_{k + 1}, y_{k + 1}$ and auxiliary sequence $(\rho_k)_{k \ge 1}, (\alpha_k)_{k \ge 2}$ by the procedures: 
        \begin{align*}
            & x_{k + 1} = y_k - L^{-1}\mathcal G_Ly_k, 
            \\
            \\
            & \text{find } \rho_{k}: 0 < \rho_{k} < \alpha_{k}^{-2}, 
            \\
            & 
            \alpha_{k + 1} = 
            \frac{1}{2}\left(
                \frac{\mu}{L} - \rho_{k}\alpha_{k}^2 
                +
                \sqrt{(\rho_{k}\alpha_{k}^2 - \mu/L)^2 + 4\rho_{k}\alpha_{k}^2}
            \right), 
            \\
            & 
            y_{k + 1} = 
            x_{k + 1} + 
            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
        \end{align*}
        In the special case $\mu = 0$, the momentum term can be represented without relaxation parameter $\rho_k$: 
        $$
            (\forall k \ge 1)\quad \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}} 
            = \alpha_{k + 1}(\alpha_k^{-1} - 1).  
        $$
    \end{definition}
    \begin{remark}
        % \textcolor{red}
        % {
        % There exists a choice of $\rho_k \in (0, 1], \mu = 0$ such that the above algorithm is equivalent to Chambolle, Dossal 2015 \cite{chambolle_convergence_2015}. 
        % When $\rho_k = 1$, this becomes just FISTA \cite{beck_fast_2009}. 
        % When $L > \mu > 0$, then choosing $\rho_k = 1$ yields equation 
        % \begin{align*}
        %     L \alpha_{k + 1}^2 = (1- \alpha_{k + 1})L \alpha_k^2 + \alpha_{k + 1} \mu. 
        % \end{align*}
        % Here, if we assume sequence $\alpha_k$ is constant, then $\alpha_k = \sqrt{\mu/L}$ is a solution to the above iterative equation. 
        % Substituting it back to the momentum form of R-WAPG, we recover the V-FISTA algorithm, which appears as (10.7.7) in Beck's Book \cite{beck_first-order_2017}. 
        % }
    \end{remark}

@@

    \begin{lemma}[Specialize convergence claim]\label{lemma:special-rwapg-convergence-claim}

    \end{lemma}
    \begin{lemma}[First example sequence]
        Choose any $a \ge 2$. 
        Define $\forall k \ge 1$ the sequence $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ by 
        \begin{align*}
            \alpha_k &= \alpha/(k + 1), 
            \\
            \rho_k &= \frac{(k + 1)(k + a)^2}{ak(k + a + 1)}. 
        \end{align*}
        Then $\alpha_k, \rho_k$ satisfies Definition \ref{def:rwapg-seq}. 
        It is a valid choice of sequence for the R-WAPG algorithm, which means that they satisfy: 
    \end{lemma}

>>>>

    \subsection{Contributions}
        Our contributions are two folds, theoretical and practical. 
        Nesterov's acceleration extrapolate $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} = (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''. 
        The choices for $\theta_k$ varies. 
        In Chamboolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ gives strong weak convergence of the iterates $x_k$ in Hilbert space. 
        In Beck \cite{beck_first-order_2017}, it has constant $\theta_t = (\sqrt{\kappa} - 1)/(\sqrt{\kappa} + 1)$ where $\kappa = \mu/L$. 
        \par
        Firstly, we relaxed the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:example_algorithm} and showed an upper bound of the optimal gap. 
        Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences that satisfy
        \begin{align*}
            \alpha_0 &\in (0, 1], 
            \\
            \alpha_k &\in (\mu/L, 1) \quad (\forall k \ge 1), 
            \\
            \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0). 
        \end{align*}
        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wagp-convergence}, \ref{prop:r-wapg-momentum-repr}, we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
        \begin{align*}
            \mathcal O\left(
                \left(
                    \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
                \right)
                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
            \right). 
        \end{align*}
        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces perfectly to the a variant proposed in Chambolle Dossal \cite{chambolle_convergence_2015} and it has the same convergence claim as in the literatures. 
        And when $\rho_k = 1$, R-WAPG reduces perfectly to V-FISTA by Beck \cite{beck_first-order_2017} if $\mu > 0$ and FISTA if $\mu = 0$ and the convergence claim is consistent with the literatures. 
        \par
        Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG''. 
        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ with minimal computational cost. 
        We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart. 
    \subsection{Prior works}

@@

\section{Formulation of R-WAPG and its convergence rates}
    The sole focus of this section is Definition \ref{def:wapg}.
    It describes the R-WAPG algorithm which generates iterates $(x_k, y_k, v_k)$ and admits potential convergence claim using Proposition \ref{prop:stepwise-lyapunov}. 
    It introduces the procedures of making the sequence $\alpha_k \in (0, 1)$ which assists with claiming convergence of the algorithm using Proposition \ref{prop:stepwise-lyapunov} by connecting them together. 
    \begin{definition}[R-WAPG sequence]\label{def:rwapg-seq}\;\\
        Assume $0 \le \mu < L$. 
        The sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge1}$ are valid for R-WAPG all the following holds: 
        \begin{align*}
            \alpha_0 &\in (0, 1], 
            \\
            \alpha_k &\in (\mu/L, 1) \quad (\forall k \ge 1), 
            \\
            \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0). 
        \end{align*}
    \end{definition}
    \begin{observation}\label{obs:r-wapg-observation-1}
        The following is true: 
        \begin{enumerate}
            \item $\rho_k > 0$ for all $k \ge 0$. 
            \item $\forall k \ge 1: L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 +\mu\alpha_k$. 
        \end{enumerate}

        % If $\alpha_1 \in (0, 1)$ which is true by $\gamma_1 \in (0, L]$, then the entire sequence $\alpha_k \in (0, 1)$. 
        % Suppose inductively that $\alpha_{k - 1}, \rho_{k - 1}$ are given such that they satisfy $\alpha_{k -1} \in (0, 1)$ and $0 < \rho_{k - 1} \alpha_{k - 1}^2 < 1$. 
        % Solving the quadratic $L\alpha_k^2=(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2 + \mu \alpha_k$ for $\alpha_k$ yields candidates. 
        % \begin{align*}
        %     \alpha_k &= 
        %     \frac{1}{2}\left(
        %         \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
        %         \pm
        %         \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
        %     \right). 
        % \end{align*}
        % Choosing the positive sign which is the larger one of the roots of the quadratic. 
        % We have $\alpha_k > 0$ because: 
        % \begin{align*}
        %     \alpha_k &=
        %     \frac{1}{2}\left(
        %         \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
        %         +
        %         \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
        %     &\ge 
        %     \frac{1}{2}\left(
        %         \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
        %         +
        %         \left|\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L\right|
        %     \right) + \alpha_{k - 1}\sqrt{\rho_{k - 1}}
        %     & > 0. 
        % \end{align*}
        % On the last strict inequality we used the fact that $\rho_{k - 1}> 0, \alpha_{k - 1} > 0$. 
        % An upper bound can be identified by using inductive hypothesis and considering: 
        % \begin{align*}
        %     \alpha_k &= 
        %     \frac{1}{2}\left(
        %         \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
        %         +
        %         \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
        %     &<
        %     \frac{1}{2}\left(
        %         \frac{\mu}{L} + 
        %         \sup_{x \in (0, 1)}
        %         \left\lbrace
        %             -x + \sqrt{(x - \mu/L)^2 + 4x}
        %         \right\rbrace
        %     & \le \frac{1}{2}\left(
        %         \mu/L + \max\left(\mu/L, -1 + \sqrt{(1 - \mu/L)^2 + 4}\right)
        %     \right) \le 1. 
        % \end{align*}
        % Going to the first inequality, we used $\rho_{k - 1} \alpha_{k - 1}^2 < 1$ to get the strict inequality. 
        % Going from the second to the third inequality, we maximized $\mu/L$ by monotone increasing of linear function and the square root function. 
        % Therefore, inductively, $\alpha_k \in (0, 1)$ holds. 
        % However, the limit of $\alpha_k$ could be 1. 

@@

        Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Definition \ref{def:rwapg-seq}. 

@@

            \gamma_k &:= \rho_{k -1}L\alpha_{k - 1}^2, 
            \hat \gamma_{k + 1} & := (1 - \alpha_k)\gamma_k + \mu \alpha_k = L\alpha_k^2, 

@@

    \begin{observation}\label{obs:r-wapg-observation-2}

@@

        For all $k \ge 1$, the algorithm chains together the sequence of $(\hat \gamma_{k+1})_{k \ge 1}$ and $(\gamma_k)_{k \ge 1}$ in Definition \ref{prop:stepwise-lyapunov} through the equalities: 
            \hat \gamma_{k + 1} 
            &= L\alpha_k^2 
            &= (1 - \alpha_k)\gamma_k + \alpha_k \mu
            &= (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 + \alpha_k \mu
            &= (1 - \alpha_k)\rho_{k - 1}\hat \gamma_{k} + \alpha_k \mu. 
        The third equality from Observation \ref{obs:r-wapg-observation-1}. 

@@

                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})

@@

        $\hat \gamma_2 = (1 - \alpha_1)\gamma_1 + \mu \alpha_1$ is true by Observation \ref{obs:r-wapg-observation-1}. 
        Observe that $R_2$ is defined in the same manner as in Proposition \ref{prop:stepwise-lyapunov} with k = 1 so we can invoke Proposition \ref{prop:stepwise-lyapunov}, and it gives: 
            & F(x_{2}) - F(x^*) + R_2 + \frac{L \alpha_1^2}{2}\Vert v_{2} - x^*\Vert^2
            & = F(x_{2}) - F(x^*) + R_2 + \frac{\hat \gamma_{2}}{2}\Vert v_{2} - x^*\Vert^2
            & \hat \gamma_2 = L \alpha_1^2 , \text{ Definition \ref{def:wapg}}

@@

            & \quad \text{By Proposition \ref{prop:stepwise-lyapunov}}
                F(x_1) - F(x^*) + R_1 + \frac{L\rho_{0}\alpha_{0}^2}{2}\Vert v_1 - x^*\Vert^2
            &= \max\left(\rho_0, 1\right)
                F(x_1) - F(x^*) + R_1 + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2

@@

        Next, for all $k = 2, 3, \cdots, N$, from Observation \ref{obs:r-wapg-observation-2}: 
            \hat \gamma_{k + 1} = L\alpha_{k}^2 
            &=(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2 + \mu\alpha_k
            &= (1 - \alpha_k)\gamma_k + \mu\alpha_k. 

@@

        The definition of $R_k$ given is the same as in Proposition \ref{prop:stepwise-lyapunov} hence we can use Proposition \ref{prop:stepwise-lyapunov} to un roll recursively for all $k \ge 1$: 

@@

            F(x_{k + 1}) - F^* + R_{k + 1} + \frac{\hat\gamma_{k + 1}}{2}\Vert v_{k + 1} - x^*\Vert^2 
            F(x_{k + 1}) - F^* + R_{k + 1} + \frac{L \alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2

@@

            F(x_{k + 1}) - F^* +

@@

    \subsection{Narrowing it down}
        \begin{proposition}[First equivalent representation of R-WAPG]\label{prop:wapg-first-equivalent-repr}\;\\
            If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}). 
            Then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$, and for all $k\ge 1$ they are algebraically equivalent to
            \begin{align*}
                & 
                y_{k} = 
                \left(
                    1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
                \right)^{-1}
                \left(
                    v_{k} + 
                    \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
                \right), 
                \\
                & x_{k + 1} = 
                y_k - L^{-1} \mathcal G_L y_k, 
                \\
                & v_{k + 1} = 
                \left(
                    1 + \frac{\mu}{L \alpha_k - \mu}
                \right)^{-1}
                \left(
                    v_k + 
                    \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
            \end{align*}

@@

            On the third $\iff$, we can assume $\alpha_k \neq \mu/L\;  \forall k \ge 1$ because from Definition \ref{def:rwapg-seq}: $\alpha_k \in (\mu/L, 1)$ for all $k \ge 1$. 
            % On the third $\iff$, we can assume $\alpha_k \neq \mu/L\; \forall k \ge 2$ because if $\alpha_k = \mu/L$ were impossible, it then has
            % \begin{align*}
            %     L \alpha_k^2 - \alpha_k\mu &= 
            %     (1 - \alpha_k)L \rho_{k - 1}\alpha_{k - 1}^2 = 0 \implies \alpha_{k - 1} = 0. 
            % \end{align*}
            % Which contradict $\alpha_{k - 1} \in (0, 1)\; \forall k \ge 2$ because $\alpha_1 \in (0, 1)$ is given to satisfy the condition in the base case, and $\alpha_k \in (0, 1)\; \forall k \ge 2$ by justifications in Observation \ref{obs:r-wapg-observation-1}. 

@@

            Assume $\mu < L$ and let $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ given by Definition \ref{def:rwapg-seq}. 
            Initialize any $x_1, v_1$ in $\RR^n$. 
            For $k = 1, 2, \cdots $, the algorithm generates sequence of vector iterates $(y_{k}, v_{k + 1}, x_{k + 1})_{k \ge 1}$ by: 

@@

                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 

@@

            Let iterates $(y_k, x_{k}, v_{k})_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge 0}$ be given by Definition \ref{def:r-wapg-intermediate}. 

@@

@@

        Given any $(x_1, v_1)$ in $\RR^n$. 

@@

        Let the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k\ge 0}$ be given by Definition \ref{def:rwapg-seq}. 

@@

            x_{k + 1} + (\alpha_k^{-1} -1)(x_{k + 1} - x_k). 

@@

    \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
        For any $y_1 = x_1 \in \RR^n$, $(\rho_k)_{k \ge 0}, (\alpha_k)_{k\ge 0}$ given by Definition \ref{def:rwapg-seq}. 
        The algorithm generates iterates $x_{k + 1}, y_{k + 1}$ For $k = 1, 2, \cdots $ by the procedures: 
        \begin{align*}
            & x_{k + 1} = y_k - L^{-1}\mathcal G_Ly_k, 
            \\
            & 
            y_{k + 1} = 
            x_{k + 1} + 
            \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
        \end{align*}
        In the special case where $\mu = 0$, the momentum term can be represented without relaxation parameter $\rho_k$: 
        $$
            (\forall k \ge 1)\quad \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}} 
            = \alpha_{k + 1}(\alpha_k^{-1} - 1).  
        $$
    \end{definition}
    \begin{remark}
        % \textcolor{red}
        % {
        % There exists a choice of $\rho_k \in (0, 1], \mu = 0$ such that the above algorithm is equivalent to Chambolle, Dossal 2015 \cite{chambolle_convergence_2015}. 
        % When $\rho_k = 1$, this becomes just FISTA \cite{beck_fast_2009}. 
        % When $L > \mu > 0$, then choosing $\rho_k = 1$ yields equation 
        % \begin{align*}
        %     L \alpha_{k + 1}^2 = (1- \alpha_{k + 1})L \alpha_k^2 + \alpha_{k + 1} \mu. 
        % \end{align*}
        % Here, if we assume sequence $\alpha_k$ is constant, then $\alpha_k = \sqrt{\mu/L}$ is a solution to the above iterative equation. 
        % Substituting it back to the momentum form of R-WAPG, we recover the V-FISTA algorithm, which appears as (10.7.7) in Beck's Book \cite{beck_first-order_2017}. 
        % }
    \end{remark}

@@

    \begin{lemma}[First specialized R-WAPG sequence]\label{lemma:special-rwapg-convergence-claim}

    \begin{lemma}[Inverted Chambolle, Dossal 2015 sequence]
        Choose any $a \ge 2$.
        Define $\forall k \ge 1$ the sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ by 
        \begin{align*}
            \alpha_k &= a/(k + a), 
            \\
            \rho_k &= \frac{(k + a)^2}{(k + 1)(k + a + 1)}. 
        \end{align*}
        If $\mu = 0$, then $\alpha_k, \rho_k$ satisfies Definition \ref{def:rwapg-seq}. 
        It is a valid choice of sequence for the R-WAPG algorithm and it has $\rho_k \ge 1$ for all $k \ge 0$. 
    \end{lemma}
    \begin{proof}
